[Re] Multiple dynamical modes of thalamic relay neurons: rhythmic bursting and intermittent phase-locking

### 2016-06-14 article/article.tex
Revised version

\documentclass[10pt,a4paper,onecolumn]{article}
% \usepackage[utf8]{inputenc}
\usepackage{marginnote}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{authblk,etoolbox}
\usepackage{titlesec}
\usepackage{calc}
\usepackage{hyperref}
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor=
{
      Owen Petchey,
      Marco Plebani,
      Frank Pennekamp,
  },
            pdftitle=
{
[Re] Chaos in a long-term experiment with a plankton community
},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=blue,
            pdfborder={0 0 0}}
\urlstyle{same}
\usepackage{tcolorbox}
\usepackage{ragged2e}
\usepackage{fontspec}
\usepackage{fontawesome}
\usepackage{caption}
\usepackage{listings}
\lstnewenvironment{code}{\lstset{language=Haskell,basicstyle=\small\ttfamily}}{}

@@

\usepackage[
  backend=biber,
%  style=alphabetic,
%  citestyle=numeric
]{biblatex}
\bibliography{article.bib}

@@

% --- Document ----------------------------------------------------------------
\title{[Re] Chaos in a long-term experiment with a plankton community}

    \usepackage{authblk}
                        \author[1]{Owen Petchey}
                    \author[1]{Marco Plebani}
                    \author[1]{Frank Pennekamp}
                            \affil[1]{Institute of Evolutionary Biology and Environmental Studies, University
of Zurich, Zurich, Switzerland}

\date{\vspace{-5mm}
      \sffamily \small \href{mailto:owen.petchey@ieu.uzh.ch}{owen.petchey@ieu.uzh.ch}}

@@

\begin{rebox}
\sffamily {\bfseries A reference implementation of}
\small
\begin{flushleft}
\begin{itemize}
    \item[→] Benincà, E., Huisman, J., Heerkloss, R., Jöhnk, K.D., Branco, P., Van
Nes, E.H., Scheffer, M. \& Ellner, S.P. (2008) Chaos in a long-term
experiment with a plankton community. Nature, 451, 822--825 DOI:
10.1038/nature06512
  \end{itemize}\par
\end{flushleft}
\end{rebox}

\section{Draft article}\label{draft-article}

@@

The original paper describes analyses of fluctuations in the abundance
of organisms in a plankton community derived from the Baltic Sea, housed
in a laboratory environment. The length of the time series (samples
every few days for 2,300 days) allowed for analyses revealing that the
observed dynamics exhibited characteristics consistent with chaos
produced by non-linear species interactions. The article concludes that
stability is not required for persistence of complex food webs, and that
long-term prediction of abundances may be fundamentally impossible. The
demonstration of chaotic dynamics and limited forecast horizons (sensu
\textcite{Petchey2015}) is important in the field of ecology, since the
ability to predict dynamics is an open question with considerable
applied importance \textcite{Petchey2015} \textcite{Mouquet2015}.

@@

This reproduction started with the raw data (source given below) and
used information from the original paper, the supplementary information
\href{http://www.nature.com/nature/journal/v451/n7180/extref/nature06512-s1.pdf}{the
Supplement to the Nature paper}, and communications with Elisa Benincà,
who provided for comparison digitised data from the original article,
and Stephen Ellner, who provided code and data used to produce results
in the original paper. Use of this data and code in this reproduction is
indicated below.

\subsection{Scope of the reproduction}\label{scope-of-the-reproduction}

An attempt was made to reproduce the majority of the results in the
original article. Instances where we did not attempt to reproduce a
result are detailed below.

\subsection{The data}\label{the-data}

The data are available as an Excel file supplement to
\href{http://onlinelibrary.wiley.com/doi/10.1111/j.1461-0248.2009.01391.x/abstract}{an
Ecology Letters publication} \textcite{Beninca2009}. The Excel file
contains several datasheets. Two were particularly important, as they
were the source of the raw data (one contains original species
abundances, the other the nutrient concentrations). We saved these two
datasheets, without any alteration, as comma separated value (csv) text
files. In the code associated with this reproduction, these data files
are read from the associated github repository. Another datasheet
contained transformed data (we also saved this as csv file, in order to
use it in this reproduction). We also received a dataset direct from
Steve Ellner, see below for details.

The original abundance dataset contains a duplicated date: 28/10/1996
(row 709 and 710 in excel sheet). We changed this (in R) to 26/10/1996,
making the observation occur half way between the two surrounding dates.
The original Protozoa variable in the original dataset contains some
numbers with a comma (instead of period) as the decimal separator; these
were changed to periods.

\subsection{Reproduction environment}\label{reproduction-environment}

The R language and environment for statistical computing and graphics
was used to make the reproduction. Additional R packages required are
specified in the code associated with this reproduction. The code for
making the analyses and figures presented in this reproduction resides
in an R markdown document, as well as a source file containing some
required functions. Some of the code takes several minutes to run, so an
intermediate data file is provided with results from this code.

@@

\subsection{Population dynamics}\label{population-dynamics}

The reproduced populations dynamics were very similar to those in figure
1b-g of the original publication (figure \ref{fig:dynamics}). As most
analyses were performed on fourth root transformed values, we plot
these, rather than raw abundances with a y-axis break as in the original
article.

\begin{figure}[htbp]
\centering
\includegraphics{figures/obs_pop_dyn.pdf}
\caption{\label{fig:dynamics}Observed population dynamics.}
\end{figure}

\subsection{Data transformations}\label{data-transformations}

The original publication states that long sequences of zeros were
removed from time series prior to transformation and further analysis.
We removed zeros by matching the removals to those in the transformed
version of the data in the published Excel file mentioned above.
Transformation steps were:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Interpolation to create equally spaced observations in time series.
\item
  Fourth root transformation.
\item
  Detrending of five of the time series.
\item
  Rescaling to zero mean and unit standard deviation.
\end{enumerate}

The reproduced transformed data closely matched the published
transformed data (figure \ref{fig:trans_comp1}).

\begin{figure}[htbp]
\centering
\includegraphics{figures/zero_rem_trans_comparison.pdf}
\caption{\label{fig:trans_comp1}Comparison of published transformed data
with reproduced transformed data. The red line is the 1:1 line.}
\end{figure}

\subsection{Correlations among species
abundances}\label{correlations-among-species-abundances}

Correlations among species abundances presented in Table 1 of the
original article closely matched our reproduced correlations, calculated
from the transformed data with zeros removed (figure
\ref{fig:corr_comp}). Deviations between the original and reproduced
correlations are relatively small (less than 0.072 units) and
infrequent.

\begin{figure}[htbp]
\centering
\includegraphics{figures/correlation_comparison.pdf}
\caption{\label{fig:corr_comp}Comparison of calculated correlations
among species abundances in the original article and this reproduction.}
\end{figure}

Highlighted in the text of the original paper were: negative
correlations of picophytoplankton with protozoa, and of
nanophytoplankton both with rotifers and calanoid copepods, positive
correlation of picophytoplankton with calanoid copepods, negative
correlation between bacteria and ostracods, and positive correlation
between bacteria and phosphorus. All of these correlations were at least
qualitatively reproduced.

\subsection{Spectral analyses}\label{spectral-analyses}

Spectral analyses in the original paper were presented graphically in
figures S3 (raw spectrograms) and S4 (Welch periodograms). The original
article states: ``fluctuations covered a range of different
periodicities'', and ``picophytoplankton, rotifers and calanoid copepods
seemed to fluctuate predominantly with a periodicity of about 30 days.''
Our reproduced spectra (not shown here, but code provided) were a
reasonably close match to the spectra in the original article.

\subsection{Lyapunov exponents by direct
method}\label{lyapunov-exponents-by-direct-method}

Reproduced divergence rates (figure \ref{fig:divergence}) and therefore
Lyapunov exponents (figure \ref{fig:LE_comparison}) were somewhat
different from those in the original article. The original article
states: ``the distance between initially nearby trajectories increased
over time, and reached a plateau after about 20--30 days''. The
reproduced results are consistent with this statement. The original
article also stated that the analyses ``yielded significantly positive
Lyapunov exponents of strikingly similar value for all species (Fig. 3;
mean exponent = 0.057 per day, s.d. = 0.005 per day, n = 9)''.
Reproduced exponents had very similar mean value, but had larger
standard deviation (mean = 0.060 and s.d. = 0.014).

\begin{figure}[htbp]
\centering
\includegraphics{figures/div_rate.pdf}
\caption{\label{fig:divergence}Reproduced divergence rates and Lyapunov
exponents (figure 3 in the original article).}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{figures/LE_comparison.pdf}
\caption{\label{fig:LE_comparison}Comparison of original and reproduced
directly estimated Lyapunov exponents.}
\end{figure}

\subsection{Lyapunov exponents by indirect
method}\label{lyapunov-exponents-by-indirect-method}

The data received directly from Stephen Ellner (file
`interp\_short\_allsystem\_newnames.csv' in the reproduction repository)
was interpolated, but without zeros removed. The reproduced interpolated
data, without zeros removed, matched closely this data (figure
\ref{fig:trans_comp2}).

\begin{figure}[htbp]
\centering
\includegraphics{figures/repro_ellner_comp.pdf}
\caption{\label{fig:trans_comp2}Comparison of interpolated data provided
by Ellner with reproduced interpolated data (no removal of zeros). The
red line is the 1:1 line.}
\end{figure}

The original paper reported a global Lyapunov exponent calculated via
two modelling approaches (neural network and generalised additive models
{[}GAMs{]}). Only the GAM approach was reproduced, with the assistance
of code donated by Stephen Ellner. The original article obtained a
global Lyapunov exponent of λ=0.08 day-1. The reproduced value was 0.04.
We did not reproduce the bootstrapping used to give confidence intervals
around this estimate.

\subsection{Predictability decay}\label{predictability-decay}

The article stated: ``For short-term forecasts of only a few days, most
species had a high predictability of R2 = 0.70 -- 0.90 (Fig. 2).
However, the predictability of the species was much reduced when
prediction times were extended to 15--30days.'' The reproduced
predictabilities, which were calculated from the GAMs, were consistent
with these qualitative statements, though were quantitatively different
(\ref{fig:prediction_distance}). We did not reproduce the predictability
estimates for linear models.

\begin{figure}[htbp]
\centering
\includegraphics{figures/prediction_distance.pdf}
\caption{\label{fig:prediction_distance}Predictability (correlation
between predicted and observed abundances) and prediction distance
(days) (figure 2 in the original article). Reproducted data in red, and
data from original publication in black.}
\end{figure}

>>>>

\documentclass[10pt,a4paper,onecolumn]{article}
% \usepackage[utf8]{inputenc}
\usepackage{marginnote}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{authblk,etoolbox}
\usepackage{titlesec}
\usepackage{calc}
\usepackage{hyperref}
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor=
{
      Georgios Detorakis,
  },
            pdftitle=
{
[Re] Multiple dynamical modes of thalamic relay neurons: rhythmic bursting
        and intermittent phase-locking
},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=blue,
            pdfborder={0 0 0}}
\urlstyle{same}
\usepackage{tcolorbox}
\usepackage{ragged2e}
\usepackage{fontspec}
\usepackage{fontawesome}
\usepackage{caption}
\usepackage{listings}
\usepackage{float,lscape}
\usepackage{xcolor,colortbl}
\usepackage{amssymb,amsmath,array,amsthm}
\usepackage{marvosym}
\usepackage{array}

\makeatletter
\newcommand{\thickhline}{%
    \noalign {\ifnum 0=`}\fi \hrule height 1pt
    \futurelet \reserved@a \@xhline
}
\newcolumntype{"}{@{\hskip\tabcolsep\vrule width 1pt\hskip\tabcolsep}}
\makeatother

\definecolor{Gray}{gray}{0.75}
\definecolor{LightGray}{gray}{0.95}
\lstnewenvironment{code}{\lstset{language=Haskell,basicstyle=\small\ttfamily}}{}

@@

\usepackage[
  backend=biber,
%  style=alphabetic,
%  citestyle=numeric
]{biblatex}
\bibliography{detorakis-2016.bib}

@@

% --- Document ----------------------------------------------------------------
\title{[Re] Multiple dynamical modes of thalamic relay neurons: 
        rhythmic bursting and intermittent phase-locking}

    \usepackage{authblk}
                        \author[1]{Georgios Detorakis}
                        \affil[1]{ Department of Cognitive Sciences, UC Irvine, CA, USA}

\date{\vspace{-5mm}
    \sffamily \small \href{mailto:gdetorak@uci.edu}{gdetorak@uci.edu}}

@@

\begin{rebox}
\sffamily {\bfseries A reference implementation of}
\small
\begin{flushleft}
\begin{itemize}
    \item[→] \emph{Multiple dynamical modes of thalamic relay neurons: rhythmic
        bursting and intermittent phase-locking}, Wang, X-J, Neuroscience,
        59(1), pg. 21--31, 1994.
  \end{itemize}\par
\end{flushleft}
\end{rebox}

@@

This work introduces a reference implementation of a neuron model 
for thalamocortical relay neurons, \cite{wang:1994} proposed by X-J Wang.
The model is conductance-based and takes advantage of an interplay between 
a T-type calcium current and a non-specific cation sag current and thus it
is able to generate spindle and delta rhythms. Another feature of this model
is the presence of an intermittent phase-locking phenomenon
where action potentials of sodium take place in a non-periodic manner, despite
the fact that they are phase-locked to the periodic input current. Finally,
the model is capable of generating tonic spike patterns. The reference 
implementation in this work, does not aim to reproduce all the results of 
the original article, but some of them in order to test if the model can be
easily reproduced and at what degree the original results are reproducible.
The source code of reference implementation is written in Python (Numpy,
Scipy, Matplotlib and Scikit-image).

@@

The model is described in this section following the paradigm of 
Nordlie et al, \cite{nordlie:2009}. Therefore, a brief description of
the model, equations, parameters and inputs are given in the form of 
tables.

Table~\ref{Table:1} provides a description of the model and Table~\ref{Table:2}
gives a glimpse of the input used during simulations. Table~\ref{Table:3}
introduces the equations of the model. The neuron model is conductance-based
consisting in four differential equations describing the dynamics of membrane
potential and the kinetics of a T-Type calcium current, a Sag current channel
and a Potassium channel. The rest currents are described by algebraic
equations. Finally, all simulations parameters are given in
Table~\ref{Table:5} and the simulations times can be found in
Table~\ref{Table:2}.

The reference implementation has been done in a Python class (Python $3.5.1$)
along with Numpy (version $1.10.4$), Scipy (version $0.17.0$) and Matplotlib
($1.5.1$). The numerical integration has been done by the \emph{ode} method 
of Scipy \emph{integrate} package taking advantage of the \emph{dopri5} 
method, which is quite close to the one used by the author of the original 
article (the author has numerically integrated the system of the four ODEs
by using a fifth-order adaptive size Runge-Kutta method). In addition, we 
provide in our implementation the choice of using \emph{BDF} or \emph{Adams}
multistep methods \cite{ascher:1998} (the choice of \emph{BDF} or \emph{Adams}
does not alter the numerical results but it's much faster than \emph{dopri5}).

All the simulations ran on a Dell OptiPlex $7040$, equipped with a sixth
generation i$7$ processor, $8$GB of physical memory and running Arch Linux
as operating system. The total execution time of simulations is $38.76$
seconds and the total consumed memory is $66$MB (if one choose to run 
the code for the parameters diagrams, the total execution time elevates 
to $3$ to $4$ days depending on the machine). Table~\ref{Table:3}, shows
all the parameters we used in order to produce our results (see Results). 
No any other implementation of this model found by the authors in order 
to make any further comparison with.  
%%
\begin{table}[!htbp]
    \centering
    \begin{tabular}{ll}
        \thickhline
        \multicolumn{2}{c}{Model Summary} \\\thickhline
        \rowcolor{Gray}
        Populations  & No population -- one neuron model \\\rowcolor{LightGray}
        Topology     & -- \\ \rowcolor{Gray}
        Connectivity & -- \\ \rowcolor{LightGray}
        Neuron Model & Hodgkin-Huxley conductance-based \\\rowcolor{Gray}
        Channel Models & \\ \rowcolor{LightGray}
        Synapse Model & -- \\ \rowcolor{Gray}
        Plasticity & -- \\ \rowcolor{LightGray}
        Input & Constant current or periodic rectangular pulses \\\rowcolor{Gray}
        Measurements & Membrane potential, channels activation, phase plane \\
        \thickhline
    \end{tabular}
    \caption{{\bfseries \sffamily Summary of the model}} 
    \label{Table:1}
\end{table}
 %%

%%
\begin{table}[!htbp]
    \centering
    \begin{tabular}{ccc}
        \thickhline
        \multicolumn{3}{c}{Simulation Time} \\ \thickhline
        Figure & Simulation Time ($s$) & Integration Step ($ms$) \\ \rowcolor{LightGray}
        $1$ & $2$, $5\times period$ & $0.05$ \\ \rowcolor{Gray}
        $2$ & $2$ & $0.05$ \\ \rowcolor{LightGray} 
        $3$ & $8$ & $0.05$  \\ \rowcolor{Gray} 
        $4$ & $2.5$ & $0.05$  \\ \rowcolor{LightGray}  
        $5$ & $2$ & $0.05$  \\ \thickhline
    \end{tabular}
    \caption{{\bfseries \sffamily Simulations Time.}}
    \label{Table:2}
\end{table}
%%

%%
\begin{table}[!htbp]
    \centering
    \begin{tabular}{llcccc}
        \thickhline
        \multicolumn{6}{c}{Input} \\\thickhline
        Figure  & Type & Form & \parbox[t]{1.5cm}{Frequency
            ($\frac{1}{P_0}$,$Hz$)} & 
            \parbox[t]{1.5cm}{Duration ($p$, $ms$)} &
            \parbox[t]{1.5cm}{Amplitude ($\mu A / cm^2$)} \\
        \thickhline \rowcolor{LightGray}
        Figure~$1$ & Periodic & 
            \includegraphics[width=0.1\textwidth]{figs/pulse.pdf} &
            \parbox[t]{1.1cm}{$5$, $10$} &
            \parbox[t]{1.1cm}{$10$, $40$} &
            \parbox[c]{0.3cm}{$-1.0$}
            \\\rowcolor{Gray}
        Figure~$2$ & Constant  & 
        \includegraphics[width=0.1\textwidth]{figs/const.pdf} &
        -- & -- & \parbox[c]{0.3cm}{$+3.0$ \\ $0.0$ $-0.5$ $-0.55$ $-0.6$ $-0.8$
        $-1.3$ $-2.1$} 
        \\\rowcolor{LightGray}
        Figure~$3$ & Constant  & 
            \includegraphics[width=0.1\textwidth]{figs/const.pdf} &
            -- & -- & \parbox[c]{0.3cm}{$-0.95$}
        \\\rowcolor{Gray}
        Figure~$4$ & Constant  & 
            \includegraphics[width=0.1\textwidth]{figs/const.pdf} &
            -- & -- & \parbox[c]{0.3cm}{$[-2,0]$}
        \\\rowcolor{LightGray}
        Figure~$5$ & Constant  & 
            \includegraphics[width=0.1\textwidth]{figs/const.pdf} &
            -- & -- & \parbox[c]{0.3cm}{$[-2,0]$} \\
        \thickhline
    \end{tabular}
    \caption{{\bfseries \sffamily Description of the applied current
        $I_{\text{app}}$ }}
    \label{Table:3}
\end{table}
%%

\begin{table}[!htbp]
    \centering
    \begin{tabular}{p{1.5cm}ll}
        \thickhline
        \multicolumn{2}{c}{Neuron Model} \\\thickhline
        \rowcolor{Gray}
        Name  &  Thalamocortical relay neuron  \\ \rowcolor{LightGray}
        Type  &  Conductance-based neuron  \\ \rowcolor{Gray}
        Membrane Potential & $
            \begin{aligned}
                C_m \frac{dV(t)}{dt} &= -I_T - I_h - I_{Na}
                  - I_K - I_{Na(P)} - I_L + I_{\text{app}}
              \end{aligned}$ \\ \rowcolor{LightGray}
        T-Type Calcium Current ($I_T$) & $
            \begin{aligned}
                I_T &= g_T \cdot s^3_{\infty}(V)\cdot h \cdot (V-V_{Ca}) \\
                s_{\infty}(V) &= \frac{1}{1 + \exp(-\frac{V+65}{7.8})} \\
                \frac{dh(t)}{dt} &= \phi_h \frac{h_{\infty}(V) - h}{\tau_h(V)} \\
                h_{\infty}(V) &= \frac{1}{1 + \exp(\frac{V-\theta_h}{k_h})} \\
                \tau_h(V) &= h_{\infty}\exp(\frac{V+162.3}{17.8}) + 20
            \end{aligned} $
            \\ \rowcolor{Gray}
        Sag Current ($I_h$) & $
            \begin{aligned}
                I_h &= g_h \cdot H^2 \cdot (V-V_h) \\
                H_{\infty}(V) &= \frac{1}{1 + \exp(\frac{V+69}{7.1})} \\
                \frac{dH(t)}{dt} &= \phi_H \frac{H_{\infty}(V) - H}{\tau_H(V)} 
            \end{aligned} $
            \\ \rowcolor{LightGray} 
        Hodgkin-Huxley Currents ($I_K$) and ($I_{Na}$) & $
            \begin{aligned}
                I_{K} &= g_K \cdot n^4 \cdot (V - V_K) \\
                \frac{dn(t)}{dt} &= \phi_n \frac{n_{\infty}(V) - n(t)}{\tau_n(V)} \\
                n_{\infty}(\sigma_K, V) &= \frac{\alpha_n(\sigma_K, V)}
                        {\alpha_n(\sigma_K, V) + \beta_n(\sigma_K, V)} \\
                \tau_n(\sigma_K, V) &= \frac{1}{\alpha_n(\sigma_K, V)
                        + \beta_n(\sigma_K, V)} \\
                \alpha_n(\sigma_K, V) &= \frac{-0.01 (V + 45.7 - \sigma_K)}
                {\exp(-0.1(V + 45.7 - \sigma_K)) - 1} \\ 
                \beta_n(\sigma_K, V) &= 0.125 \exp(-\frac{V + 55.7 -
                \sigma_K}{80}) \\
                I_{Na} &= g_{Na} \cdot m^3_{\infty}(\sigma_{Na}, V)
                    \cdot (0.85 - n) \cdot (V - V_{Na}) \\
                    m_{\infty}(V) &= \frac{\alpha_m(\sigma_{Na}, V)}
                        {\alpha_m(\sigma_{Na}, V) + \beta_m(\sigma_{Na}, V)} \\
                \alpha_m(\sigma_{Na}, V) &= -0.1 \frac{V + 29.7 - \sigma_{Na}}
                    {\exp(-0.1(V + 54.7 - \sigma{Na})) - 1} \\
                \beta_m(\sigma_{Na}, V) &= 4\exp(-\frac{V+54.7-\sigma_{Na}}{18})
            \end{aligned} $ \\ \rowcolor{Gray} 
        Persistent Sodium Currents ($I_{Na(P)}$) & $
                \begin{aligned}
                    I_{Na(P)} &= g_{Na(P)} \cdot m^3_{\infty}(\sigma_{Na(P)},
                    V) \cdot (V - V_{Na}) \\
                \end{aligned} $
            \\ \rowcolor{LightGray}
        Leak Current ($I_L$) &  $
            \begin{aligned}
                I_L &= g_L \cdot (V - V_L) \\
            \end{aligned} $ \\ \thickhline
    \end{tabular}
    \caption{{\bfseries \sffamily Description of the neuron model}} 
    \label{Table:4}
\end{table}

\begin{landscape}
\begin{table}[!htbp]
    \centering
    \begin{tabular}{p{1.5cm}lllllll}
        \thickhline
        \multicolumn{5}{c}{Model Parameters} \\\thickhline \rowcolor{Gray}
        Currents Type  & Common &  Figure $1$ & Figure $2$ & Figure $3$ &
        Figure $4$  & Figure $5$ \\
        \thickhline \rowcolor{LightGray}
        Membrane Potential & $
            \begin{aligned}
                C_m &= 1 \mu F/cm^2 \\
                V_0 &= -74mV
            \end{aligned} $ & & & \\\rowcolor{Gray}
        T-Type Calcium Current & $
            \begin{aligned}
                \phi_h &= 2 \\
                V_{Ca} &= 120mV
            \end{aligned} $ & $
            \begin{aligned}
                g_T &= 1 mS/cm^2 \\
                \theta_h &= -81 mV \\
                k_h &= 6.25 mV^{-1}
            \end{aligned} $ & $
            \begin{aligned}
                g_T &= 0.3 mS/cm^2\\
                \theta_h &= -79 mV \\
                k_h &= 5 mV^{-1}
            \end{aligned} $ & $
            \begin{aligned}
                g_T &= 0.3 mS/cm^2\\
                \theta_h &= -75 mV \\
                k_h &= 5 mV^{-1}
            \end{aligned} $ & $
            \begin{aligned}
                g_T &= 0.3/0.25/0.2 mS/cm^2\\
                \theta_h &= -81 mV \\
                k_h &= 6.25 mV^{-1}
            \end{aligned} $ & $
            \begin{aligned}
                g_T &= 1.0/0.7 mS/cm^2\\
                \theta_h &= -79 mV \\
                k_h &= 5 mV^{-1}
            \end{aligned} $ 
            \\\rowcolor{LightGray}
        Sag Current & $
            \begin{aligned}
                \phi_H &= 1 \\
                g_h &= 0.04 mS/cm^2 \\
                V_h &= -40 mV
            \end{aligned} $
        & & & \\\rowcolor{Gray}
        Hodgkin-Huxley Currents & $
            \begin{aligned}[l]
                g_K &= 30 mS/cm^2 \\
                V_K &= -80 mV \\
                \phi_n &= 28.5\\
                \sigma_K &= 10 \\
            \end{aligned} 
            \begin{aligned}[r]
                g_{Ca} &= 42 mS/cm^2 \\
                V_{Ca} &= 55 mV \\
            \end{aligned} $
            & $\sigma_{Na} = 3mV$ & $\sigma_{Na} = 6mV$ & $\sigma_{Na} = 6mV$ &
            $\sigma_{Na} = 3mV$ & $\sigma_{Na} = 6mV$
            \\\rowcolor{LightGray}
        Persistent Sodium Currents & $
            \begin{aligned}
                V_{Na(P)} &= 55 mV \\
                \sigma_{Na(P)} &= -5 \\
                g_{Na(P)} = 9 mS / cm^2 
            \end{aligned} $
            & & & & &  
            \\\rowcolor{Gray}
        Leak Current & & $
            \begin{aligned}
                g_L &= 0.1 mS/cm^2\\
                V_L &= -72 mV
            \end{aligned} $ & $
            \begin{aligned}
                g_L &= 0.12 mS/cm^2\\
                V_L &= -70 mV
            \end{aligned} $ & $
            \begin{aligned}
                g_L &= 0.08 mS/cm^2\\
                V_L &= -70 mV
            \end{aligned} $ & $
            \begin{aligned}
                g_L &= 0.08 mS/cm^2\\
                V_L &= -70 mV 
            \end{aligned} $ & $
            \begin{aligned}
                g_L &= 0.12/0.04 mS/cm^2\\
                V_L &= -70 mV 
            \end{aligned} $ \\
        \thickhline
    \end{tabular}
    \caption{{\bfseries \sffamily Simulations Parameters}} 
    \label{Table:5}
\end{table}
\end{landscape}

@@

We simulated the model described in Table~\ref{Table:4} using the parameters
given in Table~\ref{Table:5} and the corresponding input (see
Table~\ref{Table:3} for three different cases). First, we verified 
that the model is able to generate different types of burst responses such
as in figure $1$ of the original article. Thus we applied a periodic 
current pulse of $-1 \mu A/cm^2$ amplitude at several different frequencies
(in the original article frequency is referred as $\frac{1}{P_0}$) ranging
from $0.1Hz$ to $15Hz$ with a resolution (discretization) of $300$ points
(parameters diagram in Figure~\ref{Fig:1} left panel). In addition, we
picked up three specific frequencies ($\frac{1}{P_0}=10, 10, 5$ and pulse
duration $p=10, 40, 40ms$ ($\frac{p}{P_0} = 0.1, 0.4, 0.2$). 
The results are shown in Figure~\ref{Fig:1}, right panels. It is apparent that
the reference implementation can achieve the same behavior as the original
implementation. The parameters correspond to the proper behavior of the model.
%%
\begin{figure}[!htbp]
    \centering
    \includegraphics[width=1.0\textwidth]{figs/Figure1.pdf}
    \caption{{\bfseries \sffamily Responses to rhythmic hyperpolarizations.}
        We stimulate the model with a periodic pulse with frequency
        $\frac{1}{P_0}$ and we record the response of the model. All the
        parameters for this simulation are given in Table~\ref{Table:3}. 
        {\bfseries \sffamily Left Panel:} shows a range of frequencies
        $\frac{1}{P_0}$ from $0.1Hz$ to $15Hz$ versus the ratio
        $\frac{p}{P_0}$. 
        {\bfseries \sffamily Right Panels:} 
        {\bfseries \sffamily Red} color demonstrates a case where only
        subthreshold spikes are generated, when the frequency of the periodic
        pulse is $\frac{1}{P_0} = 10 Hz$ and $\frac{p}{P_0} = 0.1$. 
        {\bfseries \sffamily Blue} indicates bursts of one spike, when the
        frequency is $\frac{1}{P_0} = 10Hz$ and $\frac{p}{P_0} = 0.4$.
        {\bfseries \sffamily Black} shows a case of two spikes bursts. Here
        the frequency is $\frac{1}{P_0} = 5 Hz$ and $\frac{p}{P_0} = 0.2$.}
    \label{Fig:1}
\end{figure}
%%

In a second case, we used a steady current varying only its amplitude and 
keeping the rest parameters fixed. Hence, we used $8$ different current
amplitudes ($3, 0, -0.5, -0.55, -0.6, -0.8, -1.3$ and $-2.1 \mu A/cm^2$) and
Figure~\ref{Fig:2} illustrates the results of our simulations, which
correspond to figure $3$ of \cite{wang:1994}. Again original results
are reproducible and the model is capable of generating repetitive firing,
resting state, subthreshold oscillation, $10 Hz$ bursting, $3Hz$ bursting
and hyperpolarized steady activity. 
%%
\begin{figure}[!htbp]
    \centering
    \includegraphics[width=.8\textwidth]{figs/Figure2.pdf}
    \caption{{ \bfseries \sffamily Dynamic behavior of neuron.} Here we
    simulate the model with parameters given in Table~\ref{Table:3}. The
    only parameter that changes from panel to panel in this figure is the
    external current $I_{\text{app}}$. The jet colormap indicates the different
    current values. We observe that we get quite similar results as in the original
    article \cite{wang:1994}. For instance, we obtain, repetitive spiking when
    we apply a constant current at $3 \mu A / cm^2$, or a periodic bursting 
    response, when we apply an external current of $-1.3 \mu A /cm^2$. These
    results correspond to Figure~$3$ of \cite{wang:1994}.}
    \label{Fig:2}
\end{figure}

%%
Another test case we simulated is the one that corresponds to figure $6$ of 
\cite{wang:1994}. In this test-case the neuron receives a constant
external current at $-0.95 \frac{\mu A}{cm^2}$ and as Figure~\ref{Fig:3}
points out ``spiral chaos'' is generated as in the original article.
The parameters for this simulation are given in Table~\ref{Table:4}. 
%%
\begin{figure}[!htbp]
    \centering
    \includegraphics[width=.7\textwidth]{figs/Figure3.pdf}
    \caption{{\bfseries \sffamily ``Spiral Chaos''.} In this Figure
    we show that the model is capable of generating spiral chaos as
    it has been shown in Figure~$6$ \cite{wang:1994}. Again all the 
    parameters for this simulation are given in Table~\ref{Table:3}.
    The external current in this simulation is constant and we have 
    traced the phase portrait of the membrane potential and of the
    Sag current ($V$ vs $h$). The top panel illustrates the phase 
    portrait, the middle panel shows the membrane potential ($V$)
    and the bottom panel depicts the $h$ current over time. Our 
    results are identical to the original ones rendering 
    the model fully reproducible. }
    \label{Fig:3}
\end{figure}
%%

A fourth test case has to do with the amplitude of the injected external 
current and its relation to the frequency of the generated spike bursts. 
Therefore, we captured the data\footnote{The data are available in the
accompanying github repository of the present article.} values for the 
external current from Figure~$7$ of the original article (these are the
values represented by dots and circles in Figure $7$ and on page $27$ of
the \cite{wang:1994}) using the software
PlotDigitizer\footnote{\url{(http://plotdigitizer.sourceforge.net/})}.
Therefore, we run a simulation on the external current of the original 
article using our implementation and the results are shown in Figure 
\ref{Fig:4} upper row. Our results are pretty much the same as the ones
in Figure~$7$ of the original article. In addition, we run one more simulation
using a much higher resolution (using $200$ values of the injected current
in the range $0$ to $-2.0 \mu A/cm^2$. It is clear that the more detailed 
simulation is quantitatively similar to the simpler one but it reveals 
a more oscillatory behavior in the shape of the parameters curve. If we
superpose the two panels, we can see that the upper row is an interpolation 
of some of the data points of the bottom row.

%%
\begin{figure}[!htbp]
    \centering
    \includegraphics[width=.7\textwidth]{figs/Figure4.pdf}
    \caption{{\bfseries \sffamily Frequency and period versus steady input current.}
    {\bfseries \sffamily Top Row:} Indicates the external current (ranging from 
    $0$ to $-2 \mu A/cm^2$ versus the spike bursts frequency in $Hz$. The
    numerical values for the external current for this simulation have been
    taken from the original article (see text for more details). 
    {\bfseries \sffamily Bottom Row:} The same simulation as in the upper row,
    but with a finer discretization of the external current values range. In
    these simulations we used $200$ values for the $I_{\text{app}}$.}
    \label{Fig:4}
\end{figure}
%%

%%
\begin{figure}[!htbp]
    \centering
    \includegraphics[width=.7\textwidth]{figs/Figure5.pdf}
    \caption{{\bfseries \sffamily Symbolic patterns.}}
    \label{Fig:5}
\end{figure}
%%

Finally, we tried to simulate some of the symbolic patterns as they are 
presented in Table~$1$ of \cite{wang:1994}. Therefore, we run our
implementation using the same parameters as in \cite{wang:1994} (see 
Table~\ref{Table:5}). The results are shown in Figure~\ref{Fig:5}, where
black dots represent zeros ($0$) and red line segments represent aces ($1$).
Different patterns emerge for different values of the external current. 
For instance, the shaded area in Figure~\ref{Fig:5} indicates that the
current is between $0.0$ and $-0.75$ and thus we have only zeros in the
formed patterns.
